---
title: "TODO for the package"
---


1. Create an interactive addin, that enables to select formatting options;

2. Write unit tests.

3. Insert link [label](link_location)

4. Insert image ![caption](image_location)

5. Insert image with caption (interactive input through Shiny):
```{r}
fig_id = sub("\\.","_",
             paste0("fig_ID__", (as.double(Sys.time()))))
```
```{r fig_ID_, fig.align='center', fig.cap=CAPTION,  echo=FALSE, }
# Figure location
knitr::include_graphics("image_location")

# Figure caption/name/description
CAPTION = "The_caption_of_your_figure_comes_here..."
```

6. Write function to check if there is a space before and after the selection
(for %>% and similar operators)

7. Add possibility not to add list bullets and numbers to the empty rows.

8. FIXME: qmd_remove_list() does not remove this list correctly in this situation:
```
- 1.
- 2.
- 3.
- 4.
- 5.
```

9.  qmd_list() add:
     1. Ability to skip empty lines;
     2. Ability to continue numbering.
     

10. add_hash_style_heading(), qmd_heading_remove()
Application of "insert H1" addin in a row results in removed rows only on seccond time:
```
          1

#           1

# 1
```
Fixit or document the behavior.

11. New feature: add `\`  at the end of the line as break line symbol (the same as two spaces `  `)

12. Add reference-like (interactive) addin for links and images:
```
[text][id]

[id]: url "name"
```

13. Add indentation style code blocks: starts after blank line with indentation of 4 spaces and ends at not indented line.
